Interval Probability for Fuzzy Quantum Theories

### 2016-06-20 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} updates...

Notice that if the last condition is replaced by equal sign, these
conditions will be exactly the same as the conditions in lemma~\ref{lem:quantumProbabilityMeasure}
which is equivalent to the Born rule as in corollary~\ref{cor:Gleason's}.
Therefore, it is reasonable to believe these conditions should be
equivalent to a interval-valued Born rule.

When we pick $\mathscr{I}=\left\{ \left[x,x\right]\middle|x\in\left[0,1\right]\right\} $,
for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
we can define a corresponding quantum \emph{$\mathscr{I}$}-interval-valued
probability measure~$\mu':\events\rightarrow\mathscr{I}$ by $\mu'\left(E\right)=\left[\mu\left(E\right),\mu\left(E\right)\right]$.
In this sense, every usual quantum probability measure can be considered
as a quantum interval-valued probability measure. There are more interesting
examples as we now show.

>>>>

Notice that if the last condition is replaced by the equal sign, these
conditions will be exactly the same as the conditions in lemma~\ref{lem:quantumProbabilityMeasure}
which is equivalent to the Born rule as in corollary~\ref{cor:Gleason's}.
Therefore, it is reasonable to believe these conditions should be
equivalent to a interval-valued Born rule.

When we pick $\mathscr{I}=\left\{ \left[x,x\right]\middle|x\in\left[0,1\right]\right\} $,
for any quantum probability measure~$\tensor*[_{\left[0,1\right]}]{\mu}{}:\events\rightarrow\left[0,1\right]$,
we can define a corresponding quantum \emph{$\mathscr{I}$}-interval-valued
probability measure~$\tensor*[_{\mathscr{I}}]{\mu}{}:\events\rightarrow\mathscr{I}$
by $\tensor*[_{\mathscr{I}}]{\mu}{}\left(E\right)=\left[\tensor*[_{\left[0,1\right]}]{\mu}{}\left(E\right),\tensor*[_{\left[0,1\right]}]{\mu}{}\left(E\right)\right]$.
In this sense, every usual quantum probability measure can be considered
as a quantum interval-valued probability measure. There are more interesting
examples as we now show.

\begin{example}[Quantum three-value interval-valued probability
measure] We consider three intervals\emph{ }$\left[0,0\right]$,
$\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$
and $\left[1,1\right]$ are called \imposs~and \necess~as before,
and \emph{$\left[0,1\right]$} is called \unknown~because it provides
no information. For any Hilbert space and any quantum probability
measure~$\tensor*[_{\left[0,1\right]}]{\mu}{}:\events\rightarrow\left[0,1\right]$,
we can define a interval-valued probability measure~$\tensor*[_{\mathscr{I}}]{\mu}{}:\events\rightarrow\mathscr{I}$
by 
\[
\tensor*[_{\mathscr{I}}]{\mu}{}(E)=\iota\left(\tensor*[_{\left[0,1\right]}]{\mu}{}(E)\right)\textrm{ ,}
\]
where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is defined by
\[
\iota(x)=\begin{cases}
\necess & \textrm{, if }x=1\textrm{ ;}\\
\imposs & \textrm{, if }x=0\textrm{ ;}\\
\unknown & \textrm{, otherwise.}
\end{cases}
\]
$\iota$ has two interested properties 
\begin{eqnarray*}
\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right) & = & 1\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)\\
\iota\left(\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\right) & \subseteq & \sideset{_{\mathscr{I}}}{_{i}}\sum\iota\left(x_{i}\right)\textrm{ ,}
\end{eqnarray*}
where $x$ and $\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\in\left[0,1\right]$.
By applying these two properties, it is easy to verify $\tensor*[_{\mathscr{I}}]{\mu}{}$
is a quantum \emph{$\mathscr{I}$}-interval-valued probability measure.\qed\end{example}
